\vspace{-0.25em}\thetitle

### 2009-07-31 paper.tex
...

We are not the first researchers to apply linear techniques to the behavior of network traffic.
Lakhina~\emph{et~al.}~\cite{Lakhina04} apply principal component analysis (\caps{PCA})---which is computationally equivalent to \caps{SVD}---to the aggregate packet count traversing between ingress and egress points in Internet transit networks over time.
Their purpose for this application is to detect network traffic anomalies, but in the process, they introduce the concept of ``eigenflows'':
the principal components (\emph{c.f.} singular vectors) of aggregate traffic time series.
De Oliveira~\emph{et~al.}~\cite{DeOliveira06} further the application to \caps{PCA} to ingress-egress aggregate traffic volume, which the literature terms ``origin-destination flows,'' by classifying the principal components into three classes:
periodic components, peaked components, and noise components.
The same sorts of analysis have be extended by several other researchers~\cite{Babiarz06,Juva08}.
While some of the techniques are similar, such as \caps{SVD} and \caps{PCA}, and the terminology seems suggests similarity---all talk about ``flows''---the reality is that this research is a significant departure.
These earlier approaches analyze and forecast aggregate traffic volume in transit networks, while our research predicts the behaviors of individual flows, in the sense of a series of packets sharing a ``5-tuple,'' rather than the transit network ``origin-destination'' pair sense.
While understanding aggregate traffic behavior in core networks is certainly useful, we believe that an even broader application exists for the detailed individual flow behavior model we propose and provide evidence for here.

>>>>

We are not the first researchers to apply linear techniques to the behavior of network traffic.
Lakhina~\emph{et~al.}~\cite{Lakhina04} apply principal component analysis (\caps{PCA})---which is computationally equivalent to \caps{SVD}---to the aggregate packet count traversing between ingress and egress points in Internet transit networks over time.
Their purpose for this application is to detect network traffic anomalies, but in the process, they introduce the concept of ``eigenflows'':
the principal components (\emph{c.f.} singular vectors) of aggregate traffic time series.
De Oliveira~\emph{et~al.}~\cite{DeOliveira06} further the application to \caps{PCA} to ingress-egress aggregate traffic volume, which the literature terms ``origin-destination flows,'' by classifying the principal components into three classes:
periodic components, peaked components, and noise components.
The same sorts of analysis have be extended by several other researchers~\cite{Babiarz06,Juva08}.
While some of the techniques are similar, such as \caps{SVD} and \caps{PCA}, and the terminology seems suggests similarity---all talk about ``flows''---the reality is that this research is a significant departure.
These earlier approaches analyze and forecast aggregate traffic volume in transit networks, while our research predicts the behaviors of individual flows, in the sense of a series of packets sharing a ``5-tuple,'' rather than the transit network ``origin-destination'' pair sense.
While understanding aggregate traffic behavior in core networks is certainly useful, we believe that even broader applications exist for the detailed individual flow behavior model we have proposed.
